The Effect of Different Writing Tasks on Linguistic Style:\\ A Case Study of the ROC Story Cloze Task

### 2017-02-05 docs/language_constraint.tex
Noah

\section{Introduction}
Writing style is expressed through a range of linguistic elements such as words, sentence structure, and rhetorical devices.
It is influenced by both personal factors such as age \cite{Schler:2006} and gender \cite{Argamon:2003}, 
by personality traits such as agreeableness and openness  \cite{Ireland:2014b},
as well as by mental states\resolved{\clinic{Avoid using ``cognitive"?}} such as sentiment \cite{Davidov:2010}, sarcasm \cite{Tsur:2010}, and deception \cite{Feng:2012}.  
In this paper, we study the extent to which writing style is affected by the nature of the writing task the writer was asked to perform, since
different tasks likely engage different cognitive processes \cite{Campbell:2003,Banerjee:2014}.

@@

We show that similar writing tasks with different constraints on the author can lead to measurable differences in people's writing style.
%We explore three  writing tasks, showing that they are distinguishable from one another using a linear classifier informed with stylistic features only. 
%Our results hint that different writing tasks impose different cognitive load on the writer, which lead to the substantial style differences.
As a case study, we present experiments   based on 
the recently introduced ROC story cloze task \cite{Mostafazadeh:2016}. 
In this task, \com{crowdsourced }authors were asked to write five-sentence self-contained stories, henceforth {\it original} stories.
%Following, 
Then, 
%the stories were given to other authors, 
each original story was given to a different author, 
who was shown only the first four sentences as a story context, 
and asked to write contrastive story endings: a {\it right} (coherent) ending, and a {\it wrong} (incoherent) ending. 
Framed as a story cloze task, the goal of this dataset is to serve as a commonsense challenge for NLP and AI research. 
\tabref{ROC-example} shows an example of an {original} story, a {coherent} story, and an {incoherent} story.

@@

\com{We show that a linear classifier informed with stylistic features can distinguish between {\it original}, {\it right} and {\it wrong}  endings to a large degree, even without looking at the story context.
Our results allow us to make a few key observations.
First, people adopt a different writing style when asked to write coherent vs.~incoherent story endings.
Second,  people change their writing style when writing the entire story on their own compared to 
writing only the final sentence for a given story context written by someone else.}

@@

While the story cloze task was originally designed to be a story understanding challenge, 
its annotation process introduced three variants of the same writing task: writing an {\it original}, {\it right} or {\it wrong} ending to a short story.
In this paper, we show that a linear classifier informed with stylistic features can distinguish between the different endings to a large degree, even without looking at the story context (64.5\%--75.6\% binary classification results).

@@

In order to further estimate the quality of our results, we also directly tackle the story cloze challenge. 
 Adapting our classifier to the task, we obtain 72.4\% accuracy, a 12.5\% increase over the previously reported state-of-the-art  \cite{Salle:2016}.
We also show that the style differences captured by our model can be combined with neural language models to make a better use of the story context. 
Our final model that combines context with stylistic features achieves
75.2\%---an additional 2.8\% gain, 15.3\% better than the best
published result.

@@

Interestingly, at the time of this submission, 10 months after the
task was first introduced, the published benchmark on this task is
still below 60\% \cite{Salle:2016}.\footnote{The LSDSem 2017 shared
  task website (\url{https://competitions.codalab.org/competitions/15333}) does report higher results (71.1\%)\roy{Tricky. Which number should we report here? leave empty?}, which are still unpublished along with the underlying methodology.}
This comes in contrast to other recent similar machine reading tasks such as CNN/DailyMail \cite{hermann2015teaching}, SNLI \cite{bowman2015large}, LAMBADA \cite{Paperno:2016} and SQuAD \cite{rajpurkar2016squad}, for which results improved dramatically over a similar or shorter period of time.
This suggests that this task is challenging and that high performance is hard to achieve.
 \resolved{\yc{SQuAD was officially published in Nov 2016. by the time the official EMNLP talk was presented, the leaderboard performance (still unpublished) was  30\% beyond the best results in the paper. Given that, the statement of this paragraph seems a bit of overkill...?} \nascomment{it sounds like Yejin is saying that on squad, there was an even faster acceleration?  or that we should change ``similar period of time'' to ``similar or shorter period of time''?}}

In addition, \citet{Mostafazadeh:2016} made substantial efforts to ensure the quality of this dataset. 
First, each pair of endings was written by the same author, which ensured that author style differences could not be used to solve the task. 
Furthermore, the authors implemented nine baselines for the task, using surface level features as well as narrative-informed ones, and showed that each of them reached roughly chance-level.
These results indicate that real understanding of text is required in order to solve the task.

\paragraph{Different writing tasks in the story cloze Task.}
Several key design decisions make this task an interesting testbed for the purpose of this paper.\resolved{\clinic{Which purpose?}}
First, the training set for the task (ROC Stories corpus) is not a
training sample in the usual sense,\footnote{I.e., the training
  instances are not drawn from a population similar to the one that future
  testing instances will be drawn from.\roy{I added \textbf{not} here, as otherwise it is confusing}}  as it contains only positive ({\it right}) samples, and not negative ({\it wrong}) ones. 
 \resolved{\yc{As far as I understand, this was intentional --- they didn't want
  people to pick up on random superfluous cues that can inevidently
  get into the data creation process, exactly the kind that our work
  picks up. Given that, stating this can be viewed as
  misunderstanding, I'm afraid.} \nascomment{We should maybe say that
  they did this intentionally and concede that our approach goes
  against the intentions of their task design.  But a task that
  insists that systems avoid using features that might encode one kind
of information (like style) is absurd.  Alternately, we could reframe
this not as ``things weren't controlled for'' but instead stick to the
facts here and just describe what they did without judgment.}}

@@

\isection{Surface Analysis of the Story Cloze Task}{Surface}
We computed several characteristics of the three types of endings: {\it original} endings (from the ROC story corpus training set), {\it right} endings and {\it wrong} endings (both from the story cloze task development set).
Our analysis  reveals several style differences between different groups. 
First, {\it original} endings are on average longer (11 words per
sentence) than {\it right} endings (8.75 words), which are in turn
slightly longer than {\it wrong} ones (8.47 words). 
Previous work have shown that sentence length is also indicative of whether a text was deceptive \cite{yancheva2013automatic,qin2004exploratory}. 
Although writing {\it wrong} sentences is not the same as lying, it is not entirely surprising to observe similar trends in both tasks.
%Furthermore, \citet{Buller:1996} suggests lying increases one's cognitive load, which in turn could affect sentence length.
%\yc{Is there psycholinguistic literature that we can cite that may have shown that cognitive burden causes writers to write shorter sentences...?}

@@

Finally, \figref{roc_word_distribution} presents the distribution of five frequent words across the different groups. 
The figure shows that {\it original} endings use coordinations (``and'') more than  {\it right} endings, and substantially more than {\it wrong} ones. %\ms{\cite{Newman:2003} found that liars use less ``contrast'' coordination, did we find that in our experiments?}.
Furthermore, {\it original} and {\it right} endings seem to prefer enthusiastic language (e.g., ``!''), while {\it wrong} endings tend to use more negative language (``hates''), similarly as deceptive text \cite{Newman:2003}.
%\yc{Again, any cogsci literature on this?} \nascomment{feels
%  Pennebaker-ish, that might be a good place to look.}
Next we show that these style differences are not anecdotal, but can be used to distinguish between the different groups of text.

@@

We train a logistic regression classifier to distinguish between different endings. 
Each feature vector is computed using the words in one ending, without considering earlier parts of the story. 
We use the following style features.

\begin{itemize}
\item\textit{\textbf{Length}.} The number of words in the sentence.
\item\textit{\textbf{Word n-grams.}} We use sequences of 1-5
  words. Following \citet{Tsur:2010} and \citet{Schwartz:2013}, we distinguish between high frequency and low frequency words. 
Specifically, we replace content words (nouns, verbs, adjectives, and adverbs), which are often low frequency, with their part-of-speech tags.
\item\textit{\textbf{Character $n$-grams.}} Character $n$-grams are one of the most useful features in identifying author style \cite{Stamatatos:2009}. 
We use character 4-grams.
\end{itemize}

@@

\isectionb{Results}
\tabref{results} shows our results.
In Experiment 1, our model obtains 64.5\%
classification accuracy, well above a (50\%-accurate) random baseline.
\clinic{How good is this?}
\yc{how about addressing above comment from the clinic by adding a commentary such as following: This result is surprising given that our model makes the prediction based only on the last sentence without looking at the story context, thus does not have sufficient information to judge the story coherency.}
For Experiment 2, our model is even stronger, at 68.5\%.
These results indicate that an author's style is affected in an
easily-detected way when she is prompted to write (1) a \emph{wrong} story ending vs.~a
\emph{right} one, or (2) finishing her own short story vs.~someone else's.
%These numbers indicate that these different writing tasks clearly impose different writing styles on authors.

We further measured whether these style effects are additive, by
classifying \emph{original} vs.~\emph{wrong} endings.  The setup is
exactly as in Experiment 2, but using \emph{wrong} endings instead of
\emph{right} ones.  The result is that the effects are somewhat
additive:  this third classifier achieves 75.6\%.
% That is, whether the style differences between {\it right} endings and {\it wrong} ones are different from the differences between {\it right} and {\it original} endings.
% We repeated Experiment 2, this time comparing between {\it original} and {\it wrong} sentences. 
% Our hypothesis is that differences would be even clearer. 
% Our results (\figref{results}) show that this is indeed the case: the classifier's accuracy jumps to 75.2\%.

@@

\begin{table}[!t]
\begin{center}
%\small
\begin{tabular}{|c|c|} \hline
{\bf Experiment} & {\bf Accuracy} \\ \hline
{\sl right vs. wrong} & 64.5\% \\ \hline
{\sl original vs. right} & 68.5\% \\ \hline
{\sl original vs. wrong} & 75.6\% \\ \hline
\end{tabular}
\end{center}
\caption{\label{results} Results of  experiments 1 ({\it right vs. wrong}) and 2 ({\it original vs. right}). 
Bottom row shows an additional experiment which classifies {\it  original} endings vs \textit{{wrong}} endings.
In all cases, our setup implies a 50\% random baseline.}
\end{table}

@@

\tabref{cloze_results} shows our results on the story cloze test
set. Our classifier obtains 72.4\% accuracy, 12.5\% higher than the
published state-of-the-art result on the task \cite{Salle:2016}\resolved{\nascomment{cite that here}}.
Importantly, unlike previous approaches, our classifier does not require the story corpus training data, and in fact doesn't even consider the first four sentences of the story in question.
These numbers further support the claim that the styles of {\it right} and {\it wrong} endings are indeed very different.

@@

\begin{table}[!t]
\begin{center}
%\small
\begin{tabular}{|l|r|} \hline
{\bf Model} & {\bf Accu} \\ \hline
$\dagger${DSSM} \cite{Mostafazadeh:2016} & 0.585 \\ 
$\dagger${LexVec} \cite{Salle:2016} & 0.599 \\ \hline\hline
%{Niko (shared task)}	& 0.700\\ 
%{tbmihaylov (shared task)} & 0.711\\ \hline\hline
$\dagger${RNN}		& 0.677 \\ 
{\bf Ours} & {\bf 0.724} \\ 
$\dagger${\bf Combined (ours + RNN)} & {\bf 0.752} \\ \hline\hline
$\dagger$Human judgment & 1.000 \\ \hline
\end{tabular}
\end{center}
\caption{\label{cloze_results}
\yc{we should change accuracy to be in 0-100\% scale to be consistent with Table 2}
Results on the test set of the  story cloze task. 
The first block are published results, 
the second block is our results.
LexVec results are taken from \cite{Speer:2016}.
%RNN is our implementation. 
Human judgement scores are taken from \cite{Mostafazadeh:2016}.
Methods marked with ($\dagger$) use the story context in order to make a prediction. 
 \resolved{\nascomment{I added 0s to ``Niko'' result
  and ``human''
  so sig. digits would line up.  if we don't have sig digits for some
  of them, make the zeros white so the numbers line up.  where did the
human judgments come from?  those are not mentioned in our text anywhere!}
}}
\end{table}

@@

\nascomment{please check the paragraph above.  we need to say how we
  use the LM before we evaluate it!  also, has anyone tried an approach like this
  before?  even if we aren't exactly replicating another paper, if
  someone else used RNNs for this task, we should credit them.}
  \roy{Ours is the first work to publish LSTM results on this dataset.}

% Eval
On its own, our neural language model performs moderately well on the story cloze test. 
%This is not surprising, as \citet{Mostafazadeh:2016} hinted  that
%simple language models are insufficient.
Selecting endings based on $p_\theta(\textrm{ending} \mid \textrm{story})$ (i.e., the numerator of
Equation~\ref{eq:ratio}), we obtained only 55\% accuracy.   The ratio
in Equation~\ref{eq:ratio} achieves 67.7\%  (see
\tabref{cloze_results}).\footnote{Further analysis of this large
  difference is out of the scope of this paper, but suggests careful
  study of suitable probabilistic inference methods for such tasks.}

@@

\subsection{Most Salient Features}
A followup question is which individual features contribute most to the classification process,
as these could shed light on the stylistic differences imposed by each of the writing tasks.

In order to answer this question, we consider the highest absolute positive and negative coefficients in the logistic regression classifier in both Experiments 1 and 2, an  approach widely used  as a method of extracting the most salient features \cite{Nguyen:2013,Burke:2013,Brooks:2013}.\footnote{Although it is worth noting that its reliability is not entirely clear \cite{Yano:2012}.}
We consider only features appearing in at least 5\% of the endings in our training set.

@@

Second, {\it right} endings will make wider use of coordination structures, as well as adjectives.
The latter might indicate that writing coherent stories imposes the authors to write more descriptive text compared to incoherent ones, 
as is the case in truthful vs.~deceptive text \cite{ott2011finding}.
Finally, we notice a few syntactic differences: {\it right} endings will more often use infinite verb structure, while {\it wrong} endings will prefer gerunds (VBG). 
\nascomment{note to self to come back
  to this after we agree on methodology.}

@@

\begin{table}[!t]
\begin{center}
%\small
\begin{tabular}{|c|c||c|c|} \hline
\textit{\textbf{Right}} & Freq. & \textit{\textbf{Wrong}}& Freq. \\ \hline
`ed .' & {\color{white}{0}}6.5\%& START NNP & 54.8\%\\ \hline
`and ' & 13.6\%& NN . & 47.5\% \\ \hline
JJ & 45.8\% & NN NN . & {\color{white}{0}}5.1\%\\ \hline
to VB & 20.1\%& VBG & 10.1\%\\ \hline
`d th' & 10.9\%& START NNP VBD & 41.9\%\\ \hline
%`ally' & 3.3\% & `hate' & {\color{white}{0}}1.9\% \\ \hline
%VBD the NN .& 2.2\% & ` hat' & {\color{white}{0}}2.0\% \\ \hline
%START RB & 3.1\% & START NNP & 54.8\% \\ \hline
%`ved ' &4.1\%&  `ated' & {\color{white}{0}}3.0\%\\ \hline
%` tim' &2.6\%&  NN . & 47.5\%\\ \hline

\end{tabular}
\end{center}
\caption{\label{exp1_features}
The top 5 most discriminative features for predicting {\it right} vs.~{\it wrong} endings,
along with their frequency in our story cloze training set.
}
\end{table}

\paragraph{Experiment 2.}
%In order to understand which features were most salient, we repeated Experiment 1, this time running SVM with L1 norm, such that it generates a sparse separating hyperplane. 
%This came at a minor cost of less than 2\% in performance compared to our L2 results (0.697 compared to 0.724).  
\tabref{exp2_features} shows the same analysis for Experiment 2.
As noted in \secref{ROC_Story}, {\it original} endings tend to be much longer, which is indeed the most salient feature for them.
This is inline with similar findings in the deception detection literature \cite{qin2004exploratory}.
An interesting observation is that exclamation marks are a strong indication for  {\it original} ending. 
This indicates that authors are more likely to show enthusiasm when writing their own text compared to ending an existing task.

Finally, when comparing the two groups of salient features from both experiments, we find an interesting trend.
Several features, such as ``START NNP'' and  ``NN .'', which indicate {\it wrong} sentences in Experiment 1, are used to predict {\it new} (i.e., {\it correct}) endings in Experiment 2. 
This indicates that, for instance, incoherent endings have a stronger tendency to begin with a proper noun compared to coherent endings, 
which in turn are more likely to do so than original endings. 
This partially explains why distinguishing between {\it original} and {\it wrong} endings is an easier task compared to the other pairs (\secref{Results}).

\setlength\tabcolsep{.15cm}
\begin{table}[!t]
\begin{center}
%\small
\begin{tabular}{|p{1.25cm}|c||p{2.9cm}|c|} \hline
\textit{\textbf{Original}} & Freq. & \textit{\textbf{New}}& Freq. \\ \hline
{\it length} & {\color{white}{.}}100.0\% & `.' & 93.0\%\\ \hline
`!' & {\color{white}{00}}6.1\%& START NNP  & 39.2\% \\ \hline
NN & {\color{white}{00}}78.9\% & START NNP VBD &29.0\% \\ \hline
RB & {\color{white}{0}}44.7\%& NN . & 42.3\% \\ \hline
`,' & {\color{white}{0}}12.7\%&  the NN . & 10.6\% \\ \hline

\end{tabular}
\end{center}
\caption{\label{exp2_features}
The top 5 most discriminative features for predicting {\it original} vs.~{\it new} ({\it right}) endings.
}
\end{table}

@@

The line of work that most resembles our work is the detection of deceptive text. 
Several researchers have used stylometric features to  predict deception 
\cite{Newman:2003,hancock2007lying,ott2011finding,Feng:2012}.
Some works even showed that writing style applied when lying is different across genders \cite{Perez:2014a,Perez:2014b}.
In this work, we have shown that an even more subtle writing task---writing {coherent} and {incoherent} story endings---imposes different styles on the author.

>>>>

\section{Introduction}
Writing style is expressed through a range of linguistic elements such as words, sentence structure, and rhetorical devices.
It is influenced by personal factors such as age \cite{Schler:2006} and gender \cite{Argamon:2003}, 
by personality traits such as agreeableness and openness  \cite{Ireland:2014b},
as well as by mental states\resolved{\clinic{Avoid using ``cognitive"?}} such as sentiment \cite{Davidov:2010}, sarcasm \cite{Tsur:2010}, and deception \cite{Feng:2012}.  
In this paper, we study the extent to which writing style is affected by the nature of the writing task the writer was asked to perform, since
different tasks likely engage different cognitive processes \cite{Campbell:2003,Banerjee:2014}.

@@

We show that similar writing tasks with different constraints on the
author can lead to measurable differences in her writing style.
%We explore three  writing tasks, showing that they are distinguishable from one another using a linear classifier informed with stylistic features only. 
%Our results hint that different writing tasks impose different cognitive load on the writer, which lead to the substantial style differences.
As a case study, we present experiments   based on 
the recently introduced ROC story cloze task \cite{Mostafazadeh:2016}. 
In this task, \com{crowdsourced }authors were asked to write five-sentence self-contained stories, henceforth {\it original} stories.
%Following, 
Then, 
%the stories were given to other authors, 
each original story was given to a different author, 
who was shown only the first four sentences as a story context, 
and asked to write two contrasting story endings: a {\it right} (coherent) ending, and a {\it wrong} (incoherent) ending. 
Framed as a story cloze task, the goal of this dataset is to serve as a commonsense challenge for NLP and AI research. 
\tabref{ROC-example} shows an example of an {original} story, a {coherent} story, and an {incoherent} story.

@@

\com{We show that a linear classifier informed with stylistic features can distinguish among {\it original}, {\it right}, and {\it wrong}  endings to a large degree, even without looking at the story context.
Our results allow us to make a few key observations.
First, people adopt a different writing style when asked to write coherent vs.~incoherent story endings.
Second,  people change their writing style when writing the entire story on their own compared to 
writing only the final sentence for a given story context written by someone else.}

@@

While the story cloze task was originally designed to be a story understanding challenge, 
its annotation process introduced three variants of the same writing task: writing an {\it original}, {\it right}, or {\it wrong} ending to a short story.
In this paper, we show that a linear classifier informed by stylistic features can distinguish between the different endings to a large degree, even without looking at the story context (64.5--75.6\% binary classification results).

@@

In order to further validate our method, we also directly tackle the
story cloze challenge \nascomment{cite the challenge?  a reader may
  not realize that there is a shared task on this}. 
 Adapting our classifier to the task, we obtain 72.4\% accuracy, a
 12.5\% increase over the previously reported state of the art  \cite{Salle:2016}.
We also show that the style differences captured by our model can be combined with neural language models to make a better use of the story context. 
Our final model that combines context with stylistic features achieves
75.2\%---an additional 2.8\% gain, 15.3\% better than the best
published result.

@@

Interestingly, at the time of this submission, 10 months after the
task was first introduced, the published benchmark on this task is
still below 60\% \cite{Salle:2016}.\footnote{The LSDSem 2017 shared
  task website
  (\url{https://competitions.codalab.org/competitions/15333}) does
  report higher results% (71.1\%)
\roy{Tricky. Which number should we report here? leave empty?}
\nascomment{leave empty for now}, which
are still unpublished along with the underlying methodology.} 
This comes in contrast to other recent similar machine reading tasks such as CNN/DailyMail \cite{hermann2015teaching}, SNLI \cite{bowman2015large}, LAMBADA \cite{Paperno:2016} and SQuAD \cite{rajpurkar2016squad}, for which results improved dramatically over a similar or shorter period of time.
This suggests that this task is challenging and that high performance is hard to achieve.
 \resolved{\yc{SQuAD was officially published in Nov 2016. by the time the official EMNLP talk was presented, the leaderboard performance (still unpublished) was  30\% beyond the best results in the paper. Given that, the statement of this paragraph seems a bit of overkill...?} \nascomment{it sounds like Yejin is saying that on squad, there was an even faster acceleration?  or that we should change ``similar period of time'' to ``similar or shorter period of time''?}}

In addition, \citet{Mostafazadeh:2016} made substantial efforts to ensure the quality of this dataset. 
First, each pair of endings was written by the same author, which
ensured that style differences between authors could not be used to solve the task. 
Furthermore, Mostafazadeh et al.~implemented nine baselines for the task, using surface level features as well as narrative-informed ones, and showed that each of them reached roughly chance-level.
These results suggest that real understanding of text is required in order to solve the task.

\paragraph{Different writing tasks in the story cloze task.}
Several key design decisions make the task an interesting testbed for the purpose of this study.\resolved{\clinic{Which purpose?}}
First, the training set for the task (ROC Stories corpus) is not a
training sample in the usual sense,\footnote{I.e., the training
  instances are not drawn from a population similar to the one that future
  testing instances will be drawn from.%\roy{I added \textbf{not}
                                %here, as otherwise it is confusing}
}  as it contains only positive ({\it right}) samples, and not negative ({\it wrong}) ones. 
 \resolved{\yc{As far as I understand, this was intentional --- they didn't want
  people to pick up on random superfluous cues that can inevidently
  get into the data creation process, exactly the kind that our work
  picks up. Given that, stating this can be viewed as
  misunderstanding, I'm afraid.} \nascomment{We should maybe say that
  they did this intentionally and concede that our approach goes
  against the intentions of their task design.  But a task that
  insists that systems avoid using features that might encode one kind
of information (like style) is absurd.  Alternately, we could reframe
this not as ``things weren't controlled for'' but instead stick to the
facts here and just describe what they did without judgment.}}

@@

\isection{Surface Analysis of the Story Cloze Task}{Surface}
We computed several characteristics of the three types of endings: {\it original} endings (from the ROC story corpus training set), {\it right} endings and {\it wrong} endings (both from the story cloze task development set).
Our analysis  reveals several style differences between different groups. 
First, {\it original} endings are on average longer (11 words per
sentence) than {\it right} endings (8.75 words), which are in turn
slightly longer than {\it wrong} ones (8.47 words). 
Previous work has shown that sentence length is also indicative of whether a text was deceptive \cite{yancheva2013automatic,qin2004exploratory}. 
Although writing {\it wrong} sentences is not the same as lying, it is not entirely surprising to observe similar trends in both tasks.
%Furthermore, \citet{Buller:1996} suggests lying increases one's cognitive load, which in turn could affect sentence length.
%\yc{Is there psycholinguistic literature that we can cite that may have shown that cognitive burden causes writers to write shorter sentences...?}

@@

Finally, \figref{roc_word_distribution} presents the distribution of five frequent words across the different groups. 
The figure shows that {\it original} endings use coordinations (``and'') more than  {\it right} endings, and substantially more than {\it wrong} ones. %\ms{\cite{Newman:2003} found that liars use less ``contrast'' coordination, did we find that in our experiments?}.
Furthermore, {\it original} and {\it right} endings seem to prefer enthusiastic language (e.g., ``!''), while {\it wrong} endings tend to use more negative language (``hates''), similarly as deceptive text \cite{Newman:2003}.
%\yc{Again, any cogsci literature on this?} \nascomment{feels
%  Pennebaker-ish, that might be a good place to look.}
Next we show that these style differences are not anecdotal, but can
be used to distinguish between the different types of story endings.

@@

We train a logistic regression classifier to categorize an ending,
either as right vs.~wrong or as original vs.~new.
Each feature vector is computed using the words in one ending, without considering earlier parts of the story. 
We use the following style features.

\begin{itemize}
\item\textit{\textbf{Length}.} The number of words in the sentence.
\item\textit{\textbf{Word $n$-grams.}} We use sequences of 1-5
  words. Following \citet{Tsur:2010} and \citet{Schwartz:2013}, we distinguish between high frequency and low frequency words. 
Specifically, we replace content words (nouns, verbs, adjectives, and adverbs), which are often low frequency, with their part-of-speech tags.
\item\textit{\textbf{Character $n$-grams.}} Character $n$-grams are one of the most useful features in identifying author style \cite{Stamatatos:2009}. 
We use character 4-grams.
\end{itemize}

@@

\isectionb{Results}
\tabref{results} shows our results.  In both experiments,
our model achieves performance well above what would be expected under
chance (50\% by design).  Noting again that our model ignores the
story context (the preceding four sentences), our model is unable to
capture any notion of coherence.   This finding provides
strong evidence that the authors' style was affected by the writing task they
were given to perform.  We further applied the model to a third task,
\emph{original} vs.~\emph{wrong (new)} endings, and even stronger
differences were apparent to the model, allowing over 75\% accuracy.

\nascomment{I rewrote this section.  old version commented out in
  latex source}
% In Experiment 1, our model obtains 64.5\%
% classification accuracy, well above a (50\%-accurate) random baseline.
% \clinic{How good is this?}
% \yc{how about addressing above comment from the clinic by adding a
%   commentary such as following: This result is surprising given that
%   our model makes the prediction based only on the last sentence
%   without looking at the story context, thus does not have sufficient
%   information to judge the story coherency.} 
% For Experiment 2, our model is even stronger, at 68.5\%.
% These results indicate that an author's style is affected in an
% easily-detected way when she is prompted to write (1) a \emph{wrong} story ending vs.~a
% \emph{right} one, or (2) finishing her own short story vs.~someone else's.
% %These numbers indicate that these different writing tasks clearly impose different writing styles on authors.

% We further measured whether these style effects are additive, by
% classifying \emph{original} vs.~\emph{wrong} endings.  The setup is
% exactly as in Experiment 2, but using \emph{wrong} endings instead of
% \emph{right} ones.  The result is that the effects are somewhat
% additive:  this third classifier achieves 75.6\%.
% % That is, whether the style differences between {\it right} endings and {\it wrong} ones are different from the differences between {\it right} and {\it original} endings.
% % We repeated Experiment 2, this time comparing between {\it original} and {\it wrong} sentences. 
% % Our hypothesis is that differences would be even clearer. 
% % Our results (\figref{results}) show that this is indeed the case: the classifier's accuracy jumps to 75.2\%.

@@

\begin{table}[!t]
\begin{center}
%\small
\begin{tabular}{|l|r|} \hline
{\bf Experiment} & {\bf Accuracy} \\ \hline
{\sl right vs. wrong} & 0.645 \\ \hline
{\sl original vs. right} & 0.685 \\ \hline
{\sl original vs. wrong} & 0.756 \\ \hline
\end{tabular}
\end{center}
\caption{\label{results} Results of  experiments 1 ({\it right
    vs.~wrong}) and 2 ({\it original vs.~right (new)}). 
The bottom row shows an additional experiment which classifies {\it
  original vs.~wrong (new)} endings.
In all cases, our setup implies a 50\% random baseline.}
\end{table}

@@

\tabref{cloze_results} shows our results on the story cloze test
set. Our classifier obtains 72.4\% accuracy, 12.5\% (absolute) higher than the
published state-of-the-art result on the task \cite{Salle:2016}\resolved{\nascomment{cite that here}}.
Importantly, unlike previous approaches, our classifier does not require the story corpus training data, and in fact doesn't even consider the first four sentences of the story in question.
These numbers further support the claim that the styles of {\it right} and {\it wrong} endings are indeed very different.

@@

\begin{table}[!t]
\begin{center}
%\small
\begin{tabular}{|l|r|} \hline
{\bf Model} & {\bf Acc.} \\ \hline
$\dagger${DSSM} \cite{Mostafazadeh:2016} & 0.585 \\ 
$\dagger${LexVec} \cite{Salle:2016} & 0.599 \\ \hline\hline
%{Niko (shared task)}	& 0.700\\ 
%{tbmihaylov (shared task)} & 0.711\\ \hline\hline
$\dagger${RNN}		& 0.677 \\ 
{\bf Ours} & {\bf 0.724} \\ 
$\dagger${\bf Combined (ours + RNN)} & {\bf 0.752} \\ \hline\hline
$\dagger$Human judgment & 1.000 \\ \hline
\end{tabular}
\end{center}
\caption{\label{cloze_results}
\yc{we should change accuracy to be in 0-100\% scale to be consistent with Table 2}
Results on the test set of the  story cloze task. 
The first block are published results, 
the second block is our results.
LexVec results are taken from \cite{Speer:2016}.
%RNN is our implementation. 
Human judgement scores are taken from \cite{Mostafazadeh:2016}.
Methods marked with ($\dagger$) use the story context in order to make a prediction. 
 \resolved{\nascomment{I added 0s to ``Niko'' result
  and ``human''
  so sig. digits would line up.  if we don't have sig digits for some
  of them, make the zeros white so the numbers line up.  where did the
human judgments come from?  those are not mentioned in our text anywhere!}
}}
\end{table}

@@

\resolved{\nascomment{please check the paragraph above.  we need to say how we
  use the LM before we evaluate it!  also, has anyone tried an approach like this
  before?  even if we aren't exactly replicating another paper, if
  someone else used RNNs for this task, we should credit them.}
  \roy{Ours is the first work to publish LSTM results on this dataset.}}

% Eval
On its own, our neural language model performs moderately well on the story cloze test. 
%This is not surprising, as \citet{Mostafazadeh:2016} hinted  that
%simple language models are insufficient.
Selecting endings based on $p_\theta(\textrm{ending} \mid \textrm{story})$ (i.e., the numerator of
Equation~\ref{eq:ratio}), we obtained only 55\% accuracy.   The ratio
in Equation~\ref{eq:ratio} achieves 67.7\%  (see
\tabref{cloze_results}).\footnote{Note that taking the logarithm of
  the expression in Equation~\ref{eq:ratio} gives the pointwise mutual
information between the story and the ending, under the language
model. \nascomment{added this to replace the hedging that was here before}}

@@

\subsection{Most Salient Features}
A follow-up question is which individual features contribute most to the classification process,
as these could shed light on the stylistic differences imposed by each of the writing tasks.

In order to answer this question, we consider the highest absolute
positive and negative coefficients in the logistic regression
classifier in both Experiments 1 and 2, an  approach widely used  as a
method of extracting the most salient features
\cite{Nguyen:2013,Burke:2013,Brooks:2013}. It is worth noting
  that its reliability is not entirely clear, since linear models like
  logistic regression can assign large coefficients to rare features \cite{Yano:2012}.
To mitigate this concern, we consider only features appearing in at least 5\% of the endings in our training set.

@@

Second, {\it right} endings will make wider use of coordination structures, as well as adjectives.
The latter might indicate that writing coherent stories inspires the authors to write more descriptive text compared to incoherent ones, 
as is the case in truthful vs.~deceptive text \cite{ott2011finding}.
Finally, we notice a few syntactic differences: {\it right} endings will more often use infinite verb structure, while {\it wrong} endings prefer gerunds (VBG).

@@

\begin{table}[!t]
\begin{center}
%\small
\begin{tabular}{|c|c||c|c|} \hline
\textit{\textbf{Right}} & Freq. & \textit{\textbf{Wrong}}& Freq. \\ \hline
`ed .' & {\color{white}{0}}6.5\%& \textsc{start} NNP & 54.8\%\\ \hline
`and ' & 13.6\%& NN . & 47.5\% \\ \hline
JJ & 45.8\% & NN NN . & {\color{white}{0}}5.1\%\\ \hline
to VB & 20.1\%& VBG & 10.1\%\\ \hline
`d th' & 10.9\%& \textsc{start} NNP VBD & 41.9\%\\ \hline
%`ally' & 3.3\% & `hate' & {\color{white}{0}}1.9\% \\ \hline
%VBD the NN .& 2.2\% & ` hat' & {\color{white}{0}}2.0\% \\ \hline
%\textsc{start} RB & 3.1\% & \textsc{start} NNP & 54.8\% \\ \hline
%`ved ' &4.1\%&  `ated' & {\color{white}{0}}3.0\%\\ \hline
%` tim' &2.6\%&  NN . & 47.5\%\\ \hline

\end{tabular}
\end{center}
\caption{\label{exp1_features}
The top 5 most heavily weighted features for predicting {\it right} vs.~{\it wrong} endings,
along with their frequency in our story cloze training set.
}
\end{table}

\paragraph{Experiment 2.}
%In order to understand which features were most salient, we repeated Experiment 1, this time running SVM with L1 norm, such that it generates a sparse separating hyperplane. 
%This came at a minor cost of less than 2\% in performance compared to our L2 results (0.697 compared to 0.724).  
\tabref{exp2_features} shows the same analysis for Experiment 2.
As noted in \secref{ROC_Story}, {\it original} endings tend to be much longer, which is indeed the most salient feature for them.
This is in line with similar findings in the deception detection literature \cite{qin2004exploratory}.
An interesting observation is that exclamation marks are a strong
indication for an  {\it original} ending. 
This suggests that authors are more likely to show or evoke enthusiasm when writing their own text compared to ending an existing task.

Finally, when comparing the two groups of salient features from both experiments, we find an interesting trend.
Several features, such as ``\textsc{start} NNP'' and  ``NN .'', which indicate {\it wrong} sentences in Experiment 1, are used to predict {\it new} (i.e., {\it correct}) endings in Experiment 2. 
This indicates that, for instance, incoherent endings have a stronger tendency to begin with a proper noun compared to coherent endings, 
which in turn are more likely to do so than original endings. 
This partially explains why distinguishing between {\it original} and {\it wrong} endings is an easier task compared to the other pairs (\secref{Results}).

\setlength\tabcolsep{.15cm}
\begin{table}[!t]
\begin{center}
%\small
\begin{tabular}{|p{1.25cm}|c||p{2.9cm}|c|} \hline
\textit{\textbf{Original}} & Freq. & \textit{\textbf{New}}& Freq. \\ \hline
{\it length} & {\color{white}{.}}100.0\% & `.' & 93.0\%\\ \hline
`!' & {\color{white}{00}}6.1\%& \textsc{start} NNP  & 39.2\% \\ \hline
NN & {\color{white}{00}}78.9\% & \textsc{start} NNP VBD &29.0\% \\ \hline
RB & {\color{white}{0}}44.7\%& NN . & 42.3\% \\ \hline
`,' & {\color{white}{0}}12.7\%&  the NN . & 10.6\% \\ \hline

\end{tabular}
\end{center}
\caption{\label{exp2_features}
The top 5 most heavily weighted features for predicting {\it original} vs.~{\it new} ({\it right}) endings.
}
\end{table}

@@

The line of work that most resembles our work is the detection of deceptive text. 
Several researchers have used stylometric features to  predict deception 
\cite{Newman:2003,hancock2007lying,ott2011finding,Feng:2012}.
Some works even showed that gender affects a person's  writing style when lying \cite{Perez:2014a,Perez:2014b}.
In this work, we have shown that an even more subtle writing task---writing {coherent} and {incoherent} story endings---imposes different styles on the author.
